A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
more CN2 results.

\begin{table}
\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error Estimate} & \textbf{Train Error Rate} & \textbf{Test Error Rate} & \textbf{Time}
\end{tabular}
\caption{Results for CN2.}
\label{tbl:results_cn2}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{ | l | l | l | l | l |}
    \hline
    \textbf{Algorithm} & \textbf{Error estimate} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    Unordered & Laplacian & 13.3 & 15.2 & 3min29sec \\ \hline
    Unordered & Naive & - & - & - \\ \hline
    Ordered & Laplacian & 0 & 17.6 & 1min45sec \\ \hline
    Ordered & Naive & 0 & 19.9 & 12min21sec \\ \hline
\end{tabular}
\caption{Results for CN2.}
\label{tbl:results_cn2}
\end{center}
\end{table}
